Well Hello There!

### 2025-08-13 index.qmd
Update

  @media screen and (max-width: 600px) {
    .tiktok-embed {
      flex: 1 1 100%; /* Full width on mobile */
      max-width: 100%; /* Full width on mobile */
    }
  }
</style>
```
::: tiktok-container
<blockquote class="tiktok-embed" cite="https://www.tiktok.com/@mentaikofries_/video/7181240142063996161" data-video-id="7181240142063996161">

@@

```{=html}
<script async src="https://www.tiktok.com/embed.js"></script>
```
## Contact Details

@@

Resume - [Download](https://raw.githubusercontent.com/mrzknrns/mrzknrns.github.io/c446afc4b2d7902cfc76a22458cbc7789d1a09d7/MARZUKI_SANIP_RESUME.pdf)

>>>>

  @media screen and (max-width: 600px) {
    .tiktok-embed {
      flex: 1 1 100%; /* Full width on mobile */
      max-width: 100%; /* Full width on mobile */
    }
  }
</style>
```

::: tiktok-container
<blockquote class="tiktok-embed" cite="https://www.tiktok.com/@mentaikofries_/video/7181240142063996161" data-video-id="7181240142063996161">

@@

```{=html}
<script async src="https://www.tiktok.com/embed.js"></script>
```

## Contact Details

@@

Resume - [Download](MARZUKI_SANIP_RESUME_Updated.pdf)
